---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![Build Status](https://travis-ci.org/vincenzocoia/powers.svg?branch=master)](https://travis-ci.org/vincenzocoia/powers)

__Note__: This R package is not mean to be "serious". It's just for teaching purposes. 
This file has been adapted from Vincenzo Coia's README file for the Powers Package. 

# powers

This is an R package that gives `sqrt()` friends by providing other power functions.


## Installation

You can install powers from github with:

First install the devtools package:
```{r gh-installation, eval = FALSE}
# install.packages("devtools")
```
Then, clone and download the powers-master documents from my github repository: [link here](https://github.com/STAT545-UBC-students/hw07-JasmineLib/tree/master)

# Functions included:
The functions included in the powers package are:  
- root()  
- square()  
- cube()  
- reciprocal()  

# Details on the Root() function:   
- this is the function made for this hw07 assignment  
- accepted inputs must be of class numeric (ie an integer, numeric vector, etc)  
- arguments are accepted in the form (x,y), where x is the entry you want the root of, and y is the specific root you want to take (see examples below).  
- if y is not specified, it will default to y = 2, to take the square root.


## Examples

You can see the vignette for more extensive use, but here's a few examples:

will take the square root of 4:
```{r example1}
powers::root(4,2)
```

will also take square root of 4: 
```{r example2}
powers::root(4)
```

will take the cube root:
```{r example3}
powers::root(27,3)
```

will take the square root of a numeric vector:
```{r example4}
powers::root(c(0.01,1,4,9))
```

logicals will coerce to numeric, and the ^1/5 root will be obtained
```{r example5}
powers::root(c(TRUE, FALSE, TRUE), 5)
```

# Another Example Using a Graph: 
```{r graph example}
library(ggplot2)
library(powers)
test_dataframe = data.frame("Cubes" = c(1,8,27,64,125,216),"Squares" = c(1,4,9,16,25,36), "Regular" = c(1,2,3,4,5,6))


#Graph without any powers functions:
ggplot(test_dataframe) +
    geom_line() +
    aes(x = Squares, y =Cubes) + 
    ggtitle("Cube Values vs. Square Values") + 
    theme_bw()

#You can also use powers functions to manipulate your data, for example to make a graph
#use the root and cube function with piping.
ggplot(test_dataframe) +
    geom_line() +
    aes(x = root(Squares), y = cube(Regular)) +  
    ggtitle("Cubes vs. square root of Squares") + 
    theme_bw()

```

## For Developers

Use the internal `pow` function as the machinery for front-end functions such as `square`, `cube`, and `reciprocal`, and `root`. 
