---
title: "Powers R Package for STAT 547"
author: "Vincenzo Coia and JasmineLib"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Powers R Package for STAT 547}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
This vignette is to document the package named Powers. This package was developped initially by Vincenzo Coia, and was subsequently updated by Jasmine as part of the STAT547 hw07.

Here, you will learn how to use the functions in this package that include square, cube, reciprocal, and root.

#Functions found within this Package:  
- square() will take the square of the numerical input  
- cube()  will take the cube of the numerical input
- reciprocal()  will take the reciprocal of the numerical input
- root()  will take the root (as specified in second argument) of the numerical input


Here is a demonstration of how we can apply these functions:

```{r}
library(powers)
square(3)
cube(3)
reciprocal(3)
root(4,2)

```


You can also call a numerical variable to these functions:
```{r}
test_var = 9
test_var2 = 3

square(test_var)
cube(test_var)
reciprocal(test_var)
root(test_var,test_var2)

```

You can enter something other than integers as well, such as a double: 

```{r}
double_test = 0.456
square(double_test)
cube(0.1)
root(0.2, double_test)
```


you can apply these functions to a list:
```{r}
test_c = c(1,2,3,4,5)
square(test_c)


```


You cannot input a non-numerical argument:
```{r}
#root("hi",1)
#root(c(1,"hi", 4), 2)
```

root() is flexible because you are able to select the root you want to take, as well as the number you want to take the root of.

```{r}
root(8,3)
root(16,2)
root(0.3, 2)
```

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

